 

### 2020-09-28 doc/manuscript/MEE_manuscript.Rmd

[Kristina J. Anderson-Teixeira^1,2^*](0000-0001-8461-9713),
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Camille Piponiot^1,2^,
Ross Alexander,
Craig D. Allen,
Raquel Alfaro-Sánchez^wl^,
Tala Awada,
Jennifer Baltzer^wl^,
Patrick Baker,
Sarayudh Bunyavejchewin,
Paolo Cherubini,
Justin Cooper,
Stuart Davies^2^,
Ryan Helcoski^1^,
[Jakub Kašpar^cz^](0000-0003-1780-6310),
Kamil Kral,
James Lutz,
Ellis Q. Margolis,
Justin Maxwell^jm^,
Sean McMahon^2^,
Helene Muller-Landau^2^,
Sabrina Russo,
[Pavel Šamonil^cz^](0000-0002-7722-8797),
Anastasia Sniderhan^wl^,
Alan J. Tepley^1,at^,
[Ivana Vašíčková^cz^](0000-0002-6070-5956), 
Mart Vlam,
Peter Zuidema

>>>>

[Kristina J. Anderson-Teixeira^1,2^*](0000-0001-8461-9713),
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Camille Piponiot^1,2^,
Ross Alexander,
Craig D. Allen,
Raquel Alfaro-Sánchez^wl^,
Tala Awada,
Jennifer Baltzer^wl^,
Patrick Baker,
Sarayudh Bunyavejchewin,
Paolo Cherubini,
Justin Cooper,
Stuart Davies^2^,
Ryan Helcoski^1^,
[Jakub Kašpar^cz^](0000-0003-1780-6310),
James Lutz,
Ellis Q. Margolis,
Justin Maxwell^jm^,
Sean McMahon^2^,
Helene Muller-Landau^2^,
Sabrina Russo,
[Pavel Šamonil^cz^](0000-0002-7722-8797),
Anastasia Sniderhan^wl^,
Alan J. Tepley^1,at^,
[Ivana Vašíčková^cz^](0000-0002-6070-5956), 
Mart Vlam,
Peter Zuidema

### 2020-09-28 doc/manuscript/tables_figures/sites_table.Rmd

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE,  escape = F)%>%
  column_spec(1, width = "2cm") %>%
  column_spec(2, width = "4cm") %>%
  column_spec(3, width = "3cm") %>%
  column_spec(6, width = "2cm") %>%
  column_spec(9, width = "2cm") %>%
  column_spec(10, width = "2cm") %>%
  column_spec(11, width = "3cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) 
```

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE,  escape = F)%>%
  column_spec(1, width = "1cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "3cm") %>%
  #column_spec(6, width = ".5cm") %>%
  column_spec(7, width = "1.4cm") %>%
  column_spec(8, width = "1cm") %>%
  #column_spec(9, width = "2cm") %>%
  column_spec(10, width = "3cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
